---
title       : Fuel Efficiency Shiny Application
subtitle    : An easy way to predict MPG for your car
author      : Deon Jacobs
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github      : 
      user: DeonJacobs
      repo: FuelEfficiencySlidify
---
<style>
.title-slide {
  background-color: #ACDBC9;
}

.title-slide hgroup > h1{
 font-family: 'Arial', 'Helvetica', sanserif; 
}

.title-slide hgroup > h1, 
.title-slide hgroup > h2 {
  color: #355C7D;
}

</style>

## Fuel efficiency for the future
<br> </br>
Although electric cars (via Tesla) are increasing daily on our roads affordability and charging infrastructure hinder widespread adoption. 
<br> </br>
Until the cost and proliferation of electric charging stations are overcome, selecting a traditional fuel efficient car is essential to limit carbon emissions. 
<br> </br>
Car manufacturer's fuel efficiency guidlines can't always be trusted, especially in light of the recent Volkswagen emission's scandal. 

--- .class #id 

## Predicting MPG using linear regression
<br> </br>
Using actual car data, spanning multiple models and timeframes, linear regression predictions can assist in chosing a fuel efficient vehicle.  
R studio provides historical sample data of a group of vehicles (mtcars), which is used to predict the miles per gallon value from its horsepower rating. The most recent car data can be sourced and used to make vehicle selection more relevant compared to the data set in Rstudio

```{r echo=FALSE}
head(mtcars)
```

--- .class #id 

## MPG Linear Regression in Action

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(UsingR)
  library(ggplot2)
  data(mtcars)
  
  g <- ggplot(mtcars, aes(x=hp, y=mpg))
  g <- g + xlab("horse power")
  g <- g + ylab("miles per gallon")
  g <- g + geom_point(size=6, colour ="black", alpha=0.2)
  g <- g + geom_point(size=5,colour = "blue", alpha=0.2)
  g <- g + geom_smooth(method = "lm", color="black")
  g
  
  fit <- lm(mpg ~ hp,data=mtcars)
  fit2 <- lm(mpg ~ I(hp - mean(hp)),data=mtcars) 
```

---

## Shiny Fuel Efficiency Application

Using the previous linear model a Shiny application was developed to predict the MPG value from a current vehicle horsepower rating. 

The link to the application can be found here: [DataProductsFuelEfficiencyApp](https://deonjacobs.shinyapps.io/DataProductsFuelEfficiency/).





